TMR: Detecting Structure in Graphical Data

### 2021-01-19 interim-report/interim-report.tex
Change to 2 columns

%packages
\usepackage[margin=0.5in]{geometry}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{mathtools}
\usepackage{parskip}
\usepackage{fancyvrb}
\usepackage{bbm}
\usepackage{algorithm}% http://ctan.org/pkg/algorithm
\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx

@@

%custom commands
\newcommand{\dft}{\mathcal{F}}
\newcommand{\idft}{\mathcal{F}^{-1}}
\newcommand{\Xcal}{\mathcal{X}}
\newcommand{\Dcal}{\mathcal{D}}
\newcommand{\cmplx}{\mathbb{C}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Gaussian}{\mathcal{N}}
\newcommand{\Gcal}{\mathcal{G}}
\newcommand{\Vcal}{\mathcal{V}}
\newcommand{\Ecal}{\mathcal{E}}
\newcommand{\pbold}{\boldsymbol{p}}
\newcommand{\sigmabold}{\boldsymbol{\sigma}}
\newcommand{\lik}{\mathcal{L}}
\newcommand{\kl}{\mathcal{D}}
\newcommand{\Integers}{\mathbb{Z}}
\newcommand{\SBM}{\textrm{SBM}}
\newcommand{\iid}{\stackrel{iid}{\sim}}
\newcommand{\one}{\mathbbm{1}}
\newcommand{\figwidth}{0.4\linewidth}

@@

@@

Proving lemma \ref{lem:kl-div} is simply a case of algebraic manipulation:
%
\begin{align}
	\log \frac{f(e/m, e, m)}{f(r, e, m)} &= e \cdot \log \frac{e/m}{r} + (m-e) \cdot \log \frac{1- e/m}{1 - r} \nonumber \\
	&= m \cdot \left( (e/m) \cdot \log \frac{e/m}{r} + (1 - e/m) \cdot \log \frac{1- e/m}{1 - r} \right) \nonumber \\
	&= m \kl \left( \textrm{Bern}(e/m) || \textrm{Bern}(r) \right) \quad \therefore \textrm{QED}
\end{align}

Thereby proving lemma \ref{lem:kl-div}. This allows us to simplify the test-statistic into a form that is more numerically stable (equation \ref{eqn:test-stat-compute-form}). However, we must simplify further still using lemma \ref{lem:kl-approx-chi}.
%
\begin{equation}
	t_n = M_\alpha \cdot \kl\left( \textrm{Bern}(\hat{p}) || \textrm{Bern}(\hat{r})\right) + 
	M_\beta \cdot \kl\left( \textrm{Bern}(\hat{q}) || \textrm{Bern}(\hat{r})\right)
	\label{eqn:test-stat-compute-form}
\end{equation}

@@

The proof requires defining $\delta(x) \coloneqq g(x) - h(x)$ and taking a Taylor expansion of $\log 1 + x$:
%
\begin{align*}
	\kl(g||h) &= \sum_{x \in \Xcal} (\delta + h) \log \left(1 + \frac{\delta}{g} \right) 
	= \sum_{x \in \Xcal} (\delta + h) \left( \frac{\delta}{h} - \frac{\delta^2}{2h^2} + O(\delta^3) \right)  \\
	&= \sum_{x \in \Xcal} \delta + \frac{1}{2} \sum_{x \in \Xcal} \frac{\delta^2}{h} + O(\delta^3) 
	= \frac{1}{2} \sum_{x \in \Xcal} \frac{\delta^2}{h} + O(\delta^3) \\
	&= \frac{1}{2} \chi^2(g||h) + O(\delta^3) \approx \frac{1}{2} \chi^2(h||g) \quad \therefore \textrm{QED}
\end{align*}
%
Where the summation over $\delta$ evaluates to 0 because $\delta$ is the difference of two valid p.m.f's which each sum to 1 over $x \in \Xcal$. We are able to neglect the $O(\delta^3)$ terms for $g$ very close to $h$. The chi-squared distance between two Bernoullis for $g = Bern(p)$ and $h = Bern(q)$ is simply:
%
\begin{equation}
\chi^2(\textrm{Bern}(p) || \textrm{Bern}(q)) = \left( \frac{p-q}{\sqrt{q(1-q)}} \right)^2
\end{equation}

@@

\begin{theorem}[$\chi^2$ test]
	For $(X, \Gcal) \sim \textrm{SBM}(n, p, W)$, given the realised graph and class labels $(X, \Gcal)$ we can perform a hypothesis test on parameters $W_\alpha$ and $W_\beta$ of the connectivity matrix $W$.
	%
	\begin{align*}
	H_0:& \quad W_{\alpha} = W_{\beta} \\
	H_1:& \quad W_{\alpha} \neq W_{\beta}
	\end{align*}
	If the log-likelihood ratio test statistic $t_n$ is computed as in equation \ref{eqn:test-stat-compute-form}, repeated here:
	%
	\begin{equation*}
		t_n \coloneqq  M_\alpha \cdot \kl\left( \textrm{Bern}(\hat{p}) || \textrm{Bern}(\hat{r})\right) + 
		M_\beta \cdot \kl\left( \textrm{Bern}(\hat{q}) || \textrm{Bern}(\hat{r})\right)
	\end{equation*}

@@

We perform a hypothesis test in the manner described by theorem \ref{theorem:hyp-test-sbm-chi} to determine whether gender influences how friends connect on Facebook. We choose to analyse SNAP egonet with id 0 (the id of the egonet is the id of the single egonode) though any choice is possible. The egonet is plotted on figure \ref{fig:ego-0-by-gender} with nodes coloured by gender. We use the Python package NetworkX \cite{networkx} for its visualisation tools. Indeed, we will discuss layout algorithms later as for now we focus on the simple hypothesis test.
%
\begin{figure}[!h]
	\centering
	\includegraphics[width=\figwidth]{ego-0-by-gender.png}
	\caption{Egonet 0 with nodes coloured by gender}
	\label{fig:ego-0-by-gender}
\end{figure}

@@

Therefore, $p_1$ is the probability that two vertices of gender-77 are connected, $q$ is the crossover probability and $p_2$ is the connection probability within the gender-78 community\footnote{Strictly speaking this is the not gender-77 community as there are a handful of vertices that do not disclose their gender to Facebook or do not fall into this binary}. The results of the hypothesis tests are given in table \ref{tab:egonet-0-hyp-tests} alongside p-values (we choose a 95\% significance level to reject the null). However, in some cases the test statistics were so extreme that the p-value saturated to 0.
%
\begin{table}[!h]
	\centering
	\begin{tabular}{c c c c c}
		$n_1$                & $n_2$                & $\hat{p_1}$ & $\hat{q}$ & $\hat{p_2}$       \\ \hline
		130 & 218 & $8.13 \times 10^{-2}$ & $7.66 \times 10^{-2}$ & $10.6 \times 10^{-2}$
	\end{tabular}
	\caption{Egonet-0 properties and parameter estimates}
	\label{tab:egonet-0-props}
\end{table}

\begin{table}[!h]
	\centering
	\begin{tabular}{cccccc}
		Test & $H_0$                & $H_1$                & p-value & $H_0$ rejected       \\ \hline
		1    & $p_1 = q$            & $p_1 \neq q$         & 0.158 &  No                \\
		2    & $p_1 = p_2$ & $p_1 \neq p_2$ & 0.000 & Yes \\
		3    & $q = p_2$ & $q \neq p_2$ &  0.000 & Yes
	\end{tabular}
	\caption{Egonet-0 hypothesis tests that gender influences friendship formation}
	\label{tab:egonet-0-hyp-tests}
\end{table}

@@

%
\begin{algorithm}
	\caption{Linearised Acyclic Belief Propagation (ABP)}
	\label{alg:lin-abp}
	\begin{algorithmic}
		\Function{ABP}{$\Ecal$, $\Vcal$, r, T}
		\State $y^{(0)}_{v' \rightarrow v} \gets \Gaussian(0, 1)$ \Comment{Initialise messages randomly}
		\For{$t \in \{1, 2 \cdots T\}$}
		\For{$(v, v') \in \Ecal$}
		\State $s^{(t-1)} \gets \frac{1}{2|E|} \sum_{(v, v') \in \Ecal} y^{(t-1)}_{v' \rightarrow v}$ \Comment{Compute average}
		\State $z^{(t-1)}_{v' \rightarrow v} \gets y^{(t-1)}_{v' \rightarrow v} - s^{(t-1)}$ \Comment{Recentre messages}
		\State $y^{(t)}_{v' \rightarrow v} \gets \sum_{(v', v'') \in \Ecal \setminus \{v\}}z^{(t-1)}_{v'' \rightarrow v'}$ \Comment{Sum incoming messages} \\
		\If {$\exists v''' \in \Vcal$ such that $(v''' \rightarrow v \rightarrow v')$ is on a cycle of length $r' \leq r$}
		\State $y^{(t)}_{v' \rightarrow v} \leftarrow y^{(t)}_{v' \rightarrow v} - \sum_{(v, v'') \in \Ecal \setminus \{v', v'''\}}z^{(t-r')}_{v'' \rightarrow v'}$ \Comment{Cyclic correction}
		\EndIf
		\EndFor
		\EndFor
		\State $\sigma_v \gets \sum_{(v, v') \in \Ecal} y^{(T)}_{v' \rightarrow v}$ \Comment{Sum incoming messages}
		\State $S \gets \{v \in \Vcal : \sigma_v > 0\}$ \Comment{Hard assignment}
		\State $S^C \gets \{v \in \Vcal : \sigma_v \leq 0\}$
		\State \textbf{return} $S, S^C$
		\EndFunction
	\end{algorithmic}
\end{algorithm}

@@

Where $\sigma_{max}$ is the largest positive value of $\sigma_v$ and $\sigma_{min}$ is the most negative. The normalised quantity has restricted range $\tilde{\sigma}_v \in [-1, +1]$ with $0$ still being the decision boundary for partitioning. We colour each vertex according to this quantity $\tilde{\sigma}_v$ and plot the graph on figure \ref{fig:abp-output-norm}. We see intuitively that ABP has worked. The blue cluster in the lower right is clearly part of the same community. Furthermore, many vertices that do not seem to belong to any cluster have uncertain classifications (the colour is close to green).
%
\begin{figure}[!h]
	\centering
	\begin{subfigure}{0.4\linewidth}
		\includegraphics[width=\linewidth]{ego-0-abp.png}
		\caption{Normalised ABP output $\tilde{\sigma}_v$ colouring vertices}
		\label{fig:abp-output-norm}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
		\includegraphics[width=\linewidth]{ego-0-abp-by-gender.png}
		\caption{Vertices grouped by hard ABP assignments and coloured by gender. In assigned community 1 ($S$ - left) we have \{58, 122\} gender-77 and gender-78 respectively and in detected community 2 ($S^C$ - right) we have \{72, 96\}}
		\label{fig:abp-output-by-gender}
	\end{subfigure}
	\caption{Egonet-0 weak recovery results}
\end{figure}

We can evaluate formally whether weak recovery has succeeded by inspecting figure \ref{fig:abp-output-by-gender} and treating gender-77 and gender-78 as the two communities of interest:
%
\begin{equation}
	\frac{|\Omega_{77} \cap S|}{|\Omega_{77}|} = \frac{58}{58+72} = 0.446
	\quad \textrm{and} \quad
	 \frac{|\Omega_{78} \cap S|}{|\Omega_{78}|} = \frac{122}{122+96} = 0.560
\end{equation}

@@

Linear regression finds the constant bias $a$ and $f \times 1$ weight vector $b$ that minimises the mean squared prediction error $\epsilon^T \epsilon / n$. The theory for linear regression is well known so omitted here (see \cite{yale-linear-regression} for a reference). We perform a linear regression using only gender and language features available in the dataset and plot the parameter coefficient in order of decreasing magnitude (figure \ref{fig:abp-output-lin-regression}).
%
\begin{figure}[!h]
	\centering
	\begin{subfigure}{0.6\linewidth}
		\includegraphics[width=\linewidth]{ego-0-abp-community-fractions.png}
		\caption{Community fractions $|\Omega_i \cap S| / |\Omega_i|$}
		\label{fig:abp-output-community-fractions}
	\end{subfigure}
	\begin{subfigure}{0.6\linewidth}
		\includegraphics[width=\linewidth]{ego-0-abp-lin-regression.png}
		\caption{Linear regression of $\tilde{\sigma}_v$ on select feature ($R^2 = 0.113$)}
		\label{fig:abp-output-lin-regression}
	\end{subfigure}
	\caption{Egonet-0 linear classifier results}
\end{figure}

@@

\nocite{*}
\printbibliography

>>>>

%packages
\usepackage[margin=0.5in]{geometry}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{mathtools}
\usepackage{parskip}
\usepackage{fancyvrb}
\usepackage{bbm}
\usepackage{algorithm}% http://ctan.org/pkg/algorithm
\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
\usepackage{multicol}

@@

%custom commands
\newcommand{\dft}{\mathcal{F}}
\newcommand{\idft}{\mathcal{F}^{-1}}
\newcommand{\Xcal}{\mathcal{X}}
\newcommand{\Dcal}{\mathcal{D}}
\newcommand{\cmplx}{\mathbb{C}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Gaussian}{\mathcal{N}}
\newcommand{\Gcal}{\mathcal{G}}
\newcommand{\Vcal}{\mathcal{V}}
\newcommand{\Ecal}{\mathcal{E}}
\newcommand{\pbold}{\boldsymbol{p}}
\newcommand{\sigmabold}{\boldsymbol{\sigma}}
\newcommand{\lik}{\mathcal{L}}
\newcommand{\kl}{\mathcal{D}}
\newcommand{\Integers}{\mathbb{Z}}
\newcommand{\SBM}{\textrm{SBM}}
\newcommand{\iid}{\stackrel{iid}{\sim}}
\newcommand{\one}{\mathbbm{1}}
\newcommand{\figwidth}{\linewidth}

@@

\begin{multicols*}{2}

@@

Proving lemma \ref{lem:kl-div} is simply a case of algebraic manipulation and is omitted here. However, this allows us to simplify the test-statistic into a form that is more numerically stable (equation \ref{eqn:test-stat-compute-form}). However, we must simplify further still using lemma \ref{lem:kl-approx-chi}.
%
\begin{equation}
	t_n = M_\alpha \kl\left( \textrm{Bern}(\hat{p}) || \textrm{Bern}(\hat{r})\right) + 
	M_\beta \kl\left( \textrm{Bern}(\hat{q}) || \textrm{Bern}(\hat{r})\right)
	\label{eqn:test-stat-compute-form}
\end{equation}

@@

The proof requires defining $\delta(x) \coloneqq g(x) - h(x)$ and taking a Taylor expansion of $\log 1 + \epsilon$:
%
\begin{align*}
	\kl(g||h) &= \sum_{x \in \Xcal} (\delta + h) \log \left(1 + \frac{\delta}{g} \right) \\
	&= \sum_{x \in \Xcal} (\delta + h) \left( \frac{\delta}{h} - \frac{\delta^2}{2h^2} + O(\delta^3) \right)  \\
	&= \sum_{x \in \Xcal} \delta + \frac{1}{2} \sum_{x \in \Xcal} \frac{\delta^2}{h} + O(\delta^3) \\
	&= \frac{1}{2} \sum_{x \in \Xcal} \frac{\delta^2}{h} + O(\delta^3) \\
	&= \frac{1}{2} \chi^2(g||h) + O(\delta^3) \approx \frac{1}{2} \chi^2(h||g) \quad \therefore \textrm{QED}
\end{align*}
%
Where the summation over $\delta$ evaluates to 0 because $\delta$ is the difference of two valid p.m.f's which each sum to 1 over $x \in \Xcal$. We are able to neglect the $O(\delta^3)$ terms for $g$ very close to $h$. The chi-squared distance between two Bernoullis for $g = Bern(p)$ and $h = Bern(q)$ is simply:
%
\begin{equation}
\chi^2(\textrm{Bern}(p) || \textrm{Bern}(q)) = \left( \frac{p-q}{\sqrt{q(1-q)}} \right)^2
\end{equation}

@@

\begin{theorem}[$\chi^2$ test]
	For $(X, \Gcal) \sim \textrm{SBM}(n, p, W)$, given the realised graph and class labels $(X, \Gcal)$ we can perform a hypothesis test on parameters $W_\alpha$ and $W_\beta$ of the connectivity matrix $W$.
	%
	\begin{align*}
	H_0:& \quad W_{\alpha} = W_{\beta} \\
	H_1:& \quad W_{\alpha} \neq W_{\beta}
	\end{align*}
	If the log-likelihood ratio test statistic $t_n$ is computed as in equation \ref{eqn:test-stat-compute-form}, repeated here:
	%
	\begin{equation*}
		t_n \coloneqq  M_\alpha \kl\left( \textrm{Bern}(\hat{p}) || \textrm{Bern}(\hat{r})\right) + 
		M_\beta \kl\left( \textrm{Bern}(\hat{q}) || \textrm{Bern}(\hat{r})\right)
	\end{equation*}

@@

We perform a hypothesis test in the manner described by theorem \ref{theorem:hyp-test-sbm-chi} to determine whether gender influences how friends connect on Facebook. We choose to analyse SNAP egonet with id 0 (the id of the egonet is the id of the single egonode) though any choice is possible. The egonet is plotted on figure \ref{fig:ego-0-by-gender} with nodes coloured by gender. We use the Python package NetworkX \cite{networkx} for its visualisation tools. Indeed, we will discuss layout algorithms later as for now we focus on the simple hypothesis test.
%
\begin{figure}[H]
	\centering
	\includegraphics[width=\figwidth]{ego-0-by-gender.png}
	\caption{Egonet 0 with nodes coloured by gender}
	\label{fig:ego-0-by-gender}
\end{figure}

@@

Therefore, $p_1$ is the probability that two vertices of gender-77 are connected, $q$ is the crossover probability and $p_2$ is the connection probability within the gender-78 community\footnote{Strictly speaking this is the not gender-77 community as there are a handful of vertices that do not disclose their gender to Facebook or do not fall into this binary}. The results of the hypothesis tests are given in table \ref{tab:egonet-0-hyp-tests} alongside p-values (we choose a 95\% significance level to reject the null). However, in some cases the test statistics were so extreme that the p-value saturated to 0.
%
\begin{table}[H]
	\centering
	\begin{tabular}{c c c c c}
		$n_1$                & $n_2$                & $\hat{p_1}$ & $\hat{q}$ & $\hat{p_2}$       \\ \hline
		130 & 218 & $8.13 \times 10^{-2}$ & $7.66 \times 10^{-2}$ & $10.6 \times 10^{-2}$
	\end{tabular}
	\caption{Egonet-0 properties and parameter estimates}
	\label{tab:egonet-0-props}
\end{table}

\begin{table}[H]
	\centering
	\begin{tabular}{cccccc}
		Test & $H_0$                & $H_1$                & p-value & $H_0$ rejected       \\ \hline
		1    & $p_1 = q$            & $p_1 \neq q$         & 0.158 &  No                \\
		2    & $p_1 = p_2$ & $p_1 \neq p_2$ & 0.000 & Yes \\
		3    & $q = p_2$ & $q \neq p_2$ &  0.000 & Yes
	\end{tabular}
	\caption{Egonet-0 hypothesis tests that gender influences friendship formation}
	\label{tab:egonet-0-hyp-tests}
\end{table}

@@

%
\begin{algorithm}[H]
	\caption{Linearised Acyclic Belief Propagation (ABP)}
	\label{alg:lin-abp}
	\begin{algorithmic}
		\Function{ABP}{$\Ecal$, $\Vcal$, r, T}
		\State $y^{(0)}_{v' \rightarrow v} \gets \Gaussian(0, 1)$
		\For{$t \in \{1, 2 \cdots T\}$ and $(v, v') \in \Ecal$}
		\State $s^{(t-1)} \gets \frac{1}{2|E|} \sum_{(v, v') \in \Ecal} y^{(t-1)}_{v' \rightarrow v}$ \Comment{average}
		\State $z^{(t-1)}_{v' \rightarrow v} \gets y^{(t-1)}_{v' \rightarrow v} - s^{(t-1)}$ \Comment{recentre}
		\State $y^{(t)}_{v' \rightarrow v} \gets \sum_{(v', v'') \in \Ecal \setminus \{v\}}z^{(t-1)}_{v'' \rightarrow v'}$ \Comment{sum} \\
		\If {$(v''' \rightarrow v \rightarrow v')$ on a cycle of length $r' \leq r$}
		\State $y^{(t)}_{v' \rightarrow v} \leftarrow y^{(t)}_{v' \rightarrow v} - \sum_{(v, v'') \in \Ecal \setminus \{v', v'''\}}z^{(t-r')}_{v'' \rightarrow v'}$
		\EndIf
		\EndFor
		\State $\sigma_v \gets \sum_{(v, v') \in \Ecal} y^{(T)}_{v' \rightarrow v}$ \Comment{sum final messages}
		\State $S \gets \{v \in \Vcal : \sigma_v > 0\}$ \Comment{hard assignment}
		\State $S^C \gets \{v \in \Vcal : \sigma_v \leq 0\}$
		\State \textbf{return} $S, S^C$
		\EndFunction
	\end{algorithmic}
\end{algorithm}

@@

Where $\sigma_{max}$ is the largest positive value of $\sigma_v$ and $\sigma_{min}$ is the most negative. The normalised quantity has restricted range $\tilde{\sigma}_v \in [-1, +1]$ with $0$ still being the decision boundary for partitioning. We colour each vertex according to this quantity $\tilde{\sigma}_v$ and plot the graph on figure \ref{fig:abp-output-norm}. We see intuitively that ABP has worked. The blue cluster in the lower right is clearly part of the same community. Furthermore, many vertices that do not seem to belong to any cluster have uncertain classifications (the colour is close to green).
%
\begin{figure}[H]
	\centering
	\begin{subfigure}{\figwidth}
		\includegraphics[width=\linewidth]{ego-0-abp.png}
		\caption{Normalised ABP output $\tilde{\sigma}_v$ colouring vertices}
		\label{fig:abp-output-norm}
	\end{subfigure}
	\begin{subfigure}{\figwidth}
		\includegraphics[width=\linewidth]{ego-0-abp-by-gender.png}
		\caption{Vertices grouped by hard ABP assignments and coloured by gender. In assigned community 1 ($S$ - left) we have \{58, 122\} gender-77 and gender-78 respectively and in detected community 2 ($S^C$ - right) we have \{72, 96\}}
		\label{fig:abp-output-by-gender}
	\end{subfigure}
	\caption{Egonet-0 weak recovery results}
\end{figure}

We can evaluate formally whether weak recovery has succeeded by inspecting figure \ref{fig:abp-output-by-gender} and treating gender-77 and gender-78 as the two communities of interest:
%
\begin{equation}
	\begin{aligned}
	\frac{|\Omega_{77} \cap S|}{|\Omega_{77}|} &= \frac{58}{58+72} = 0.446 \\
	\frac{|\Omega_{78} \cap S|}{|\Omega_{78}|} &= \frac{122}{122+96} = 0.560
	\end{aligned}
\end{equation}

@@

Linear regression finds the constant bias $a$ and $f \times 1$ weight vector $b$ that minimises the mean squared prediction error $\epsilon^T \epsilon / n$. The theory for linear regression is well known so omitted here (see \cite{yale-linear-regression} for a reference). We perform a linear regression using only gender and language features available in the dataset and plot the parameter coefficient in order of decreasing magnitude (figure \ref{fig:abp-output-lin-regression}).
%
\begin{figure}[H]
	\centering
	\begin{subfigure}{\figwidth}
		\includegraphics[width=\linewidth]{ego-0-abp-community-fractions.png}
		\caption{Community fractions $|\Omega_i \cap S| / |\Omega_i|$}
		\label{fig:abp-output-community-fractions}
	\end{subfigure}
	\begin{subfigure}{\figwidth}
		\includegraphics[width=\linewidth]{ego-0-abp-lin-regression.png}
		\caption{Linear regression of $\tilde{\sigma}_v$ on select feature ($R^2 = 0.113$)}
		\label{fig:abp-output-lin-regression}
	\end{subfigure}
	\caption{Egonet-0 linear classifier results}
\end{figure}

@@

%\nocite{*}
\printbibliography

\end{multicols*}
